Asymptotic Nonlinear Solution for Electrokinetic Flow Around an Ion-Exchange Spherical Particle

### 2012-09-21 notes/work/cubic_report.tex
Add abstract and validation

@@

>>>>

\begin{abstract}
An asymptotic nonlinear solution of electrokinetic 
migration of ion-exchange particles in an electrolyte solution 
due to the application of an external electric field is presented.
The electrokinetic transport process is
described by a system of nonlinear partial differential equations (PDE).
An asymptotic analytical solution is 
derived and validated. 
\end{abstract}

@@

\section{Validation}
The derivation above is validated using MATLAB symbolic toolbox by the code 
at \verb|symbolic/asymp.m| \cite{source}.
